%-------------------------
% Latex based Resume
% Author : Sunwoo Park
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{fontawesome5}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% % serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{5pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%----------CUSTOM COMMANDS----------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------------------------------------------------------
%--------------------RESUME STARTS HERE--------------------
%----------------------------------------------------------


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\huge Sunwoo Park} \\ \vspace{2pt}
    \small \faPhone*\;(732) 354-6764 $|$ 
    \href{mailto:sunwoo.park0203@gmail.com}{\faEnvelope\;sunwoo.park0203@gmail.com} $|$ 
    \href{https://linkedin.com/in/spark0203}{\faLinkedin\;linkedin.com/in/spark0203} $|$
    \href{https://github.com/woozzzy}{\faGithub\;github.com/woozzzy} 
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Bachelor of Science in Computer Science -- GPA: 3.8/4.0 (Highest Honors)}{Aug. 2021 -- Dec. 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Artificial Intelligence Innovations Intern}{June 2023 -- May 2024}
      {Delta Air Lines}{Atlanta, GA}
      \resumeItemListStart
        \resumeItem{Fine-tuned several W2V-BERT 2.0 models for per-language speech-to-text across 7 primary languages, halving inference latency on existing development hardware and cutting server inference costs by an estimated 30\%.}
        \resumeItem{Developed offline and on-device speech transcription and translation pipeline resulting in 6x speed up when processing real-time audio by integrating OpenAI's Whisper and Google's ML Kit models on CoreML and Swift.}
        \resumeItem{Performed technical evaluations on state-of-the-art sensor technologies from several startups to optimize aircraft de-icing processes, potentially resulting in multi-billion dollar annual savings industry-wide.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Full Stack Developer Intern}{Nov. 2022 -- Jan. 2023}
      {Eachday}{Pittsburgh, PA (Remote)}
      \resumeItemListStart
        \resumeItem{Developed mobile application in Flutter from Figma wireframes, working closely with the design team to prioritize and scope 15 core features for the initial product launch.}
        \resumeItem{Architected a serverless backend in AWS (S3, Glue, Athena, Grafana) that supported big data analytics for an estimated 1,000 daily users, leading to a 30\% reduction in operational costs and a 2x increase in processing speeds.}
        % \resumeItem{Collaborated closely with medical and buisness teams to organize product sprint cadences to meet critical conference and investor deadlines.}
      \resumeItemListEnd

    \resumeSubheading
      {Research \& Development Intern}{May 2022 -- July 2022}
      {Pentabreed}{Seoul, South Korea}
      \resumeItemListStart
        \resumeItem{Developed and deployed a full-stack MERN application for automated NFT art generation and batch minting across multiple blockchains for up to 10,000 NFTs as a part of the blockchain R\&D team.}
        % \resumeItem{Designed and implemented custom Solidity contracts, more than halving gas costs when bulk minting.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
  
%-----------Research-----------
\section{Research}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Student Researcher for "Accelerating Materials Discovery with AI" Project}{Jan. 2024 -- Dec. 2024}
      {Georgia Tech VIP Program in collaboration with Fung Group}{Atlanta, GA}
      \resumeItemListStart
        \resumeItem{Researched the use of diffusion crystal structure prediction models in a novel active learning framework to generate atomic structures from spectroscopic data, yielding successful results for simple molecules.}
        \resumeItem{Performed batch hyperparameter search on the Equiformers-v2 model for increased performance on the QM9 challenge for material science discovery, achieving 48\% decrease in test error from base parameters.}
      \resumeItemListEnd

    \resumeSubheading
      {Student Researcher for "FishStalkers" Project}{Jan. 2023 -- May 2023}
      {Georgia Tech VIP Program in collaboration with McGrath Lab}{Atlanta, GA}
      \resumeItemListStart
        \resumeItem{Trained and fine-tuned a YOLOv5 OBB model on a bespoke dataset of Lake Malawi cichilids to autonomously track the mating behavior improving precision, recall, and F1 scores by over 150\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{TagLalwizyan: POS Tagging for Endangered Creole} $|$ \emph{Python, PyTorch, HuggingFace}}{Dec. 2024}
      \resumeItemListStart
        \resumeItem{Annotated a dataset of over 200 sentences whilst developing a novel tagset tailored to the unique grammatical features of the critically endangered Louisiana Creole.}
        \resumeItem{Performed statistical evaluations of three POS tagging approaches (bidirectional LSTM, fine-tuned BERT, and transfer learning with CamemBERT), establishing a baseline for future NLP research regarding Louisiana Creole and highlighting the potential of transfer learning in low-resource languages.}
      \resumeItemListEnd
    
    \resumeProjectHeading
      {\textbf{In-Context Learning with Context Distillation on Llama3} $|$ \emph{Python, PyTorch, HuggingFace}}{May 2024}
      \resumeItemListStart
        \resumeItem{Evaluted the use of In-Context Learning alongside Context Distillation as a means of improving a text summarization task without expensive fine-tuning, achieving marginal but promising improvements in ROUGE metrics.}
      \resumeItemListEnd

    % \resumeProjectHeading
    %     {\textbf{HackGT 9: AI Music Visualizer (Track Winner)} $|$ \emph{Python, FastAPI, React, FFmpeg}}{Oct. 2022}
    %     \resumeItemListStart
    %       \resumeItem{Utilized lyric transcriptions, generated by OpenAI's Whisper model from a single audio file, as prompts for Stable Diffusion v1.5 in a frame-by-frame video generation framework that is encapsulated within a simple webapp.}
    %     \resumeItemListEnd
  \resumeSubHeadingListEnd




%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, JavaScript ES6, TypeScript, HTML/CSS, Dart, Swift, C/C++, Bash} \\
     \textbf{Frameworks}{: React, Node.js, Express, TailwindCSS, CoreML, Flutter, SwiftUI, FastAPI} \\
     \textbf{Developer Tools}{: Git, VSCode, Postman, AWS, Vim/NeoVim, Linux (Arch or Debian-based), Slurm, Nginx, Figma} \\
     \textbf{Libraries}{: PyTorch, HuggingFace, Pandas, NumPy, Matplotlib, Coqui TTS}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}